---
title: "Reproducible Pitch for Shiny Application"
author: "Shreeya"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Overview

- This application has been developed to find the best car to use for a trip.

- Application available @ https://shreeyap3.shinyapps.io/MyShinyApplication/ 

- Shiny UI.R , Server.R and other files are available @ https://github.com/shreeyap3/dataproducts 

- Shiny App presentation @ http://rpubs.com/shreeyap3/shiny-app-presentation 

## Data Used

- We used the mtcars data set for this application to get the cars details

```{r, message=FALSE}
summary(mtcars)
```

## Some Plots

Plotting the data available on the mtcars dataset

```{r, message=FALSE}
plot(mtcars)
```

## Application Functionality

- User can provide following information as INPUT
- Distance to travel
- Gasoline Price
- Maximum Gasoline Expenditure
- Car attributes like Number of Cylinder, Transmission, Horse Power etc

- Based on the above selection , the following OUTPUT is shown
- It provides the selected cars  
- Filter capability on column headers 
- Pagination based on number of results per page

Thank you


